---
title: "unrelated"
output: html_document
---
Parameter recovery for the null-hypothesis model where skill and monitoring are UNRELATED:
- the skill parameter is the same as before in random responding generating performance (S)
- monitoring accuracy is operationalized as a separate free parameter drawn randomly from a uniform distribution of (0,2) (d in the script)
- different mental models of the confidence scale (shift and scale) are included through the parameters a & b
- the goal was to see whether set and inferred parameter correlate, indicating an internally coherent model - failure to recover d'

Free parameters: S, d', a, b
Additionally the three thresholds corresponding to the 4-point rating scale are tested for correlation as well to double-check recoverability of the mental models of the scale set up by a & b

```{r}
set.seed(1996)
library(R2jags)
library(polspline)
library(extraDistr)

#task environment
ntrials <- 25 #25 questions
nCat <- 4 #4 confidence ratings

#parameter space
niterations <- 100

#the arrays that will be populated with 'true' set parameters
true_S <- c(0,c(niterations))
true_d <- c(0,c(niterations))
true_a <- c(0,c(niterations))
true_b <- c(0,c(niterations))
true_Cs <- array(0,c(niterations,nCat-1)) #saving here the simulated confidence thresholds based on priors a & b

#arrays that will be populated with inferred params
infer_S <- c(0,c(niterations))
infer_d <- c(0,c(niterations))
infer_a <- c(0,c(niterations))
infer_b <- c(0,c(niterations))
infer_Cs <- array(0,c(niterations,nCat-1)) #saving here the inferred confidence thresholds

#calling function for simulation
#setwd('/Users/Blanka/Desktop/thesis_2.0')
source("unrelated.R")

for (i in 1:niterations){
  
  #skill and d'
  S <- runif(1,1/3,1) #mean = real skill
  d <- runif(1,0,2)
  
  #scale and shift
  a <- rgamma(1,2,2)
  b <- rnorm(1,0,1)
  
  #saving them
  true_S[i] <- S
  true_d[i] <- d
  true_a[i] <- a
  true_b[i] <- b
  
  UR_sims <- UR(ntrials, nCat, S, d, a, b) #using the corresponding model function
  
  #save results of simulations as data
  O <- UR_sims$O
  R <- UR_sims$R
  true_Cs[i,] <- UR_sims$dReal
  
  #running jags on simulated data for inference
  data <- list("ntrials", "nCat", "O", "R")
  params <- c("S", "d", "a", "b", "dReal")
  samples <- jags(data, inits = NULL,params,
                model.file = "unrelated.txt",
                n.chains = 3, n.iter = 5000, n.burnin = 1000, n.thin = 1)
  
  #recording MAP values for the inferred parameters
  S.post <- samples$BUGSoutput$sims.list$S
  infer_S[i] <- density(S.post)$x[which(density(S.post)$y==max(density(S.post)$y))]
  
  d.post <- samples$BUGSoutput$sims.list$d
  infer_d[i] <- density(d.post)$x[which(density(d.post)$y==max(density(d.post)$y))]
  
  a.post <- samples$BUGSoutput$sims.list$a
  infer_a[i] <- density(a.post)$x[which(density(a.post)$y==max(density(a.post)$y))]
  
  b.post <- samples$BUGSoutput$sims.list$b
  infer_b[i] <- density(b.post)$x[which(density(b.post)$y==max(density(b.post)$y))]

  Cs1.post <- samples$BUGSoutput$sims.list$dReal[,1]
  infer_Cs[i,1] <- density(Cs1.post)$x[which(density(Cs1.post)$y==max(density(Cs1.post)$y))]
  
  Cs2.post <- samples$BUGSoutput$sims.list$dReal[,2]
  infer_Cs[i,2] <- density(Cs2.post)$x[which(density(Cs2.post)$y==max(density(Cs2.post)$y))]
  
  Cs3.post <- samples$BUGSoutput$sims.list$dReal[,3]
  infer_Cs[i,3] <- density(Cs3.post)$x[which(density(Cs3.post)$y==max(density(Cs3.post)$y))]
  
}
```

```{r}
par(mfrow=c(3,2))
plot(true_S, infer_S, main="Underlying skill variable: S", xlab="set skill parameter", ylab="inferred skill parameter")
cor.test(true_S, infer_S)

plot(true_d, infer_d, main="Underlying optimal calibration: d'", xlab="set d' parameter", ylab="inferred d' parameter")
cor.test(true_d, infer_d)

plot(true_a, infer_a, main="Scale parameter of the confidence scale: a", xlab="set scale parameter", ylab="inferred scale parameter")
cor.test(true_a, infer_a)

plot(true_b, infer_b, main="Shift parameter of the confidence scale: b", xlab="set shift parameter", ylab="inferred shift parameter")
cor.test(true_b, infer_b)

plot(true_Cs, infer_Cs, main="Confidence thresholds set by the linear regression", xlab="set thresholds", ylab="inferred thresholds")
cor.test(true_Cs, infer_Cs)
```

Looking at the relationship between the skill and d' parameter:
- null-hyp: no relationship testing whether that holds

```{r}
par(mfrow=c(2,1))
plot(true_S, true_d, main="Correlation between set skill and optimal calibration", xlab="set skill parameter", ylab="set d' parameter")
cor.test(true_S, true_d)

plot(infer_S, infer_d, main="Correlation between inferred skill and optimal calibration", xlab="inferred skill parameter", ylab="inferred d' parameter")
cor.test(infer_S, infer_d)
```

